Untrusted B2B Collaboration using the Blockchain

### 2018-07-18 paper/paper.tex
add some orchestration and choreography

>>>>

When speaking about a Buisiness Process with multiple participants, there are generally two types of perspectives the Process Model can have: Orchestrations and Choreographies.
Orchestrations view the Process from a central perspective, and contain only one main pool which the process is focused around. 
They describe the internal process of an organization represented by the pool.
External communication partners can be included as pools aswell, however their internal processes are not modeled.
This gives the model a clear state and order in which it has to be executed.
The main pool inhibits the role of a mediator or manager, dictating and guiding the execution.

In a choreography, the participants are much more independent.
There is no clear order or state, because the participants are acting and communicating independent of others.
An orchestration includes all public processes of each pool, as well as the communication between the processes.

One of the main ways our solution differs from the solution of Weber et al.~\cite{weber2016untrusted} is in the interpretation of orchestration and choreography.
Weber et al. implement choreographies by means of a central mediator/monitor contract.
Thus every step in the process is managed by this central contract.
The contract also holds an internal state of the process.
By our interpretation of the terms, this would not be a choreography but an orchestration.
Therefore we wanted to implement a solution, which models each pool seperately as their own entity, including having their own contracts.
Our goal is to decrease the amount trust needed between the communication partners.
By giving every pool their own set of contracts, we can make sure that every pool has control over the part of the process that is most relevant to them.
